---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cwrshelpr

<!-- badges: start -->
<!-- badges: end -->

`cwrshelpr` provides a collection of function for data analysis tasks at Dalhousie University's Centre for Water Resources Studies.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("bentrueman/cwrshelpr")
```
## Read and clean ICP-MS data

To read and clean ICP-MS data files generated by the Thermo Scientific iCAP-RQ, do the following. (N.B., this example uses an internal raw data file.)

```{r read-icp, message=FALSE}
library("cwrshelpr")
# example path to example raw data file
file <- list.files(
   path = system.file("extdata", package = "cwrshelpr"),
   full.names = TRUE
)
read_icp(path = file) # read and clean
```

